Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-03-01 src/tex/ms.tex
Add GW170818 corner to appendix
More comments from Will.

% Constraint on $\kappa$
Finally, the hierarchical result in Fig.~\ref{fig:corner_Gaussian} can be translated into an overall expectation for $\kappa_i$ via Eq.~\eqref{eq:generic_posterior}.
We show the result of doing this in Fig.~\ref{fig:posterior_kappa}, where we also compare to the posterior on $\kappa$ obtained by assuming a shared value across events (same result shown as a blue band in Fig.~\ref{fig:violin_kappa}).
The hierarchical measurement leads to an expectation that $\kappa_i = $\variable{output/restricted_kappa_median.txt}, whereas the shared-$\kappa$ measurement implies $\kappa = $\variable{output/generic_kappa_median.txt}, both symmetric 90\%-credible intervals around the median.

>>>>

% Constraint on $\kappa$
Finally, the hierarchical result in Fig.~\ref{fig:corner_Gaussian} can be translated into an overall expectation for $\kappa_i$ via Eq.~\eqref{eq:generic_posterior}.
We show the result of doing this in Fig.~\ref{fig:posterior_kappa}, where we also compare to the posterior on $\kappa$ obtained by assuming a shared value across events (same result shown as a blue band in Fig.~\ref{fig:violin_kappa}).
The hierarchical measurement leads to an expectation that $\kappa_i = $\variable{output/restricted_kappa_median.txt}, whereas the shared-$\kappa$ measurement implies $\kappa = $\variable{output/generic_kappa_median.txt}, both symmetric 90\%-credible intervals around the median.  \wf{It is very interesting to me that the analysis with $\mu$ and $\sigma$ provides a \emph{tighter} constraint on $\kappa$ than the one with the shared-$\kappa$ value.  @Max: maybe we should polish off that note with Katerina and Cole about the benefts / costs of doing the $\mu$-$\sigma$ analysis?  Do either of you understand how this comes about?  (I can make up some b.s.\ about the bimodal posteriors yielding a better model fit for the $\mu$-$\sigma$ analysis than the fixed-$\kappa$ analysis, but I'm not sure it will hold water.)}
